Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-06 paper.qmd
Changed the best layout PBMC

```{r}
#| label: umap-pbmc-read-best
umap_pbmc2 <- read_rds("data/pbmc3k/pbmc_umap_5_min_dist_0.8.rds")
pbmc_scaled_obj <- gen_scaled_data(
  data = umap_pbmc2)
umap_pbmc_scaled_best <- pbmc_scaled_obj$scaled_nldr

@@

trimesh_removed_pbmc_best <- ggplot() + 
  geom_point(
    data = umap_pbmc_scaled_best_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.3#,
    #color = "#999999"
  ) +
    geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("b1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

>>>>

```{r}
#| label: umap-pbmc-read-best
umap_pbmc2 <- read_rds("data/pbmc3k/pbmc_tsne_30.rds")
pbmc_scaled_obj <- gen_scaled_data(
  data = umap_pbmc2)
umap_pbmc_scaled_best <- pbmc_scaled_obj$scaled_nldr

@@

trimesh_removed_pbmc_best <- ggplot() + 
  geom_point(
    data = umap_pbmc_scaled_best_with_cluster,
    aes(
      x = tSNE1,
      y = tSNE2,
      color = cluster
    ),
    alpha = 0.3#,
    #color = "#999999"
  ) +
    geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("b1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```
